---
title: "Introduction to the desk-package"
output: rmarkdown::html_vignette
#toc: true
vignette: >
  %\VignetteIndexEntry{Introduction to the desk-package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
Sys.setenv(LANGUAGE="en")

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
<br/><br/>
The acronym **desk** stands for **didactic econometrics starter kit**. The primary audience of this package are students and teachers, but also casual users. **desk** ...

1. **provides visualizations that speed up the learning process and enhance the understanding of econometrics.**
2. **lowers barriers for the use of R in general.**

In following, the most important and easy-to-grasp features are presented. We show this in form of functions and mostly in resulting graphical representations.

```{r setup, echo=FALSE, results=FALSE}
suppressMessages(library(desk))
```

## Ordinary Least Squares: `ols()`
similar to lm-function (linear model, base function in R)

more appealing output

show scatter plot with regression line


## t-Test: `par.t.test()`
visualization of test results

various other tests with visualizations

same principle for other funktions


## Available data: `datasets()`
The simple command `datasets()` (without arguments, i.e. with empty brackets) shows available datasets in the package. Typing in the name shows data. Data manuals ...
```{r, echo=TRUE, results=FALSE}
datasets()
data.anscombe
my_data <- data.anscombe
```


## Simulated data: `repeat.sample()`
didactic tool for teachers

show several scatter plots (4 or 9) with different realizations


## Useful tools
`arguments()`

`rm.all()`

`new.session()`

